m0.0.1: Microxanox - ...

### 2022-03-16 inst/manuscript/manuscript_microxanox.Rmd
Some Changes to Manuscript

---
title: "m0.0.1: Microxanox - ..."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: | 
  1. set the context for and purpose of the work;
  2. indicate the approach and methods;
  3. outline the main results;
  4. identify the conclusions and the wider implications.
journal: 'Ecology and Evolution - Applications'
bibliography: manuscript_bibliography.bib
date: "`r Sys.time()`"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \doublespacing
- \usepackage{fancyhdr}
- \fancyhead{}
- \fancyfoot{}
- \fancyhead[CO,CE]{Metadata made easy - the dmdScheme approach}
- \pagestyle{fancy}

@@

Here make an overview of how conditions and parameters are specified, stored, and results stored. I think there is text in the user guide vignette that can be used (duplicated) here.

We will discuss the general structure and functiuonalit of the package without going into to mu=ch detail.

@@

## Running one simulation

@@

## Find a Steady State of the model

@@

### Replication Method
The replication method is implementad in the function `run_replication_ssfind()` which takes a parameter object as returned by the function `new_replication_ssfind_parameter()` and the number of cores for multithreading the simulation.

### Temporal Method
The temporal method involves two simulations for a particular system configuration (parameter set). In one simulation the oxygen diffusivity is *increased* in a step-wise fashion. In the other it is *decreased* in a step-wise fashion. That is, oxygen diffusivity is held at a constant level for long enough for steady state to be reach, that state is recorded, and then a slightly higher (or lower) oxygen diffusivity value is set. Hence, at that time point, the system is effectively started with initial conditions that are the state of the system in the previous time step. We hereafter term this "the temporal method".
This is implemented in the function `run_temporal_ssfind()`, which takes a parameter object as created by the function `new_temporal_ssfind_parameter()` and a number indicating the .

@@

The function `plot_dynamics()` plots a single simulation run, as returned from the `run_simulation()` function. This functio is only provided as a convenience function to provide a way to easily see the results of a simulation run. An example plot resulting from this function is shown in Figure 1.

**Please include figures so they can have captions and be cross referenced, as in the Supplement.**

![](./figures/fig1_plot_dynamics.png)

@@

Take from the user guide.

@@

Take from the partial reproduction.

>>>>

---
title: "m0.0.1: Microxanox - ..."
author:
- name: Rainer M Krug
  email: Rainer.Krug@uzh.ch & Rainer@krugs.de
  affiliation: University of Zürich
  footnote: Corresponding Author
- name: Owen L. Petchey
  email: Owen.Petchey@ieu.uzh.ch
  affiliation: University of Zürich
address:
- code: University of Zürich
  address: Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse
    190, 8057 Zurich
keywords: metadata quality; data curation; archival; long term storage; R package;
abstract: | 
  1. set the context for and purpose of the work;
  2. indicate the approach and methods;
  3. outline the main results;
  4. identify the conclusions and the wider implications.
journal: 'Ecology and Evolution - Applications'
bibliography: manuscript_bibliography.bib
date: "`r Sys.time()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \doublespacing
- \usepackage{fancyhdr}
- \fancyhead{}
- \fancyfoot{}
- \fancyhead[CO,CE]{Metadata made easy - the dmdScheme approach}
- \pagestyle{fancy}

@@

The framework used for running simulations aims at reproducibility of the results and id=s therefore build on the following points:

1. all parameter needed to run a simulation or find a stable state are contained in a single para,meter object. This object is created by using the functions `new_..._parameter()`, `new_initial_state()` and `new_strain_parameter()`. Which one of the `new_..._parameter()` functions has to be used, will be discussed imn the section  \@ref(runsim)  and in the [User Guide](LINK_NEEDED).
2. The function call `run_...(parameter)` will than run the simulation using the parameter as defined in the object `parameter`.
3. The return value of the `run_...(parameter)` function is identical to the parameter object plus an additionla slot named `results` which contains the results of the run
4. As this return value contains all parameter, it is possible to re-run the simulatuion by simply running `run_...(result)`.

The fact that the results op=bject contains all perameter needed to run the s=imulation, promotes reproducibility and makes incremental changes of individual parameters and re-running the simulations much easier.

A typical simulatiopn would look as followed:

```{r, eval = FALSE}
parameter <- new_runsim_parameter()
## manually setting certain parameter
result <- run_simulatrion(parameter)
saveRDS(result, "sim1.rds")
## Do other stuff
parameter <- loadRDS("sim1.rds")
## change some parameter
result <- run_simulatrion(parameter)
saveRDS(result, "sim2,rds")
```

## Running a simulation {#runsim}

We will now discuss the general structure and functiuonalit of the package without going into to much detail.

@@

### Running one simulation

@@

### Find a Steady State of the model

@@

#### Replication Method
The replication method is implementad in the function `run_replication_ssfind()` which takes a parameter object as returned by the function `new_replication_ssfind_parameter()` and the number of cores for multithreading the simulation.

#### Temporal Method
The temporal method involves two simulations for a particular system configuration (parameter set). In one simulation the oxygen diffusivity is *increased* in a step-wise fashion. In the other it is *decreased* in a step-wise fashion. That is, oxygen diffusivity is held at a constant level for long enough for steady state to be reach, that state is recorded, and then a slightly higher (or lower) oxygen diffusivity value is set. Hence, at that time point, the system is effectively started with initial conditions that are the state of the system in the previous time step. We hereafter term this "the temporal method".
This is implemented in the function `run_temporal_ssfind()`, which takes a parameter object as created by the function `new_temporal_ssfind_parameter()` and a number indicating the .

@@

The function `plot_dynamics()` plots a single simulation run, as returned from the `run_simulation()` function. This functio is only provided as a convenience function to provide a way to easily see the results of a simulation run. An example plot resulting from this function is shown in \@ref(fig:plot-dynamics).

```{r plot-dynamics, echo = FALSE,  include=TRUE, fig.cap='Plot of results of a simulation run using the function `plot_dynamics()`. Details can be found in the ["User Guide" section "Three strains per functional group"](LINK_NEEDED_).', fig.align="center", out.width = 500 }
knitr::include_graphics("figures/fig1_plot_dynamics.png")
```

@@

{>>Take from the user guide.<<}

@@

{>>Take from the partial reproduction.<<}
